### 2024-05-19 fantasy-football.qmd
20240519 - dual threats
20240519 - example formation
20240519 - football field diagram

![Video that provides introduction to American football.](images/football.mp4){width=100%}

@@

@@

@@

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a Running Back or Fullback), pass the ball (typically to a Wide Receiver or Tight End), or run the ball.
Quarterbacks tend to have a strong arm for throwing the ball far and accurately.

@@

The football field is rectangular and is 120 yards long and 53 1/3 yards wide.
At each end of the 120-yard field is a team's end zone.
Each end zone is 10 yards long.
Thus, the distance from one end zone to the other end zone is 100 yards.
Behind each end zone is a field goal post.

@@

The team with the ball (i.e., the offense) has four opportunities ("downs") to advance the ball 10 yards.
A team can advance the ball either by running it or passing and catching it.
At the end of a rushing play, the ball advances to wherever the ball carrier is tackled or goes out of bounds (i.e., wherever the player is "down").
At the end of a passing play, if the thrown ball is caught (i.e., a completed pass), the ball advances to wherever the ball carrier is tackled or goes out of bounds.
If the thrown ball is not caught (i.e., an incomplete pass), the ball does not advance.
Wherever the ball is advanced to dictates where the next play begins.
The yard position on the field where the next play takes place from is known as the line of scrimmage.
Neither team can cross the line the line of scrimmage until the next play begins.
To begin the play, the ball is placed on the line of scrimmage and the Center gives (or "snaps") the ball to the Quarterback.

If the team advances the ball 10 or more yards within four downs, the team is awarded a new set of downs and is given four more downs to advance the ball 10 more yards.
If the team advances the ball all the way to the other team's end zone, they score a touchdown.
If the team fails to advance the ball 10 or more yards within four downs, the team loses the ball, and the other team takes possession at that spot on the field.
There are risks of giving the other team the ball with a short distance to score.
Thus, on fourth down, instead of trying to advance the ball for a first down, a team may choose to kick a field goal—to get points—or to punt.

@@

![Video that provides introduction to fantasy football.](images/fantasyFootball.mp4){width=100%}

>>>>

![Video that Provides An Introduction to American Football.](images/football.mp4){width=100%}

@@

#### Overview {#sec-footballRosterOverview}

@@

An example formation is depicted in Figure @fig-footballFormation.

![An Example Football Formation for the Offense and Defense.](images/footballFormation.png){#fig-footballFormation}

@@

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a Running Back or Fullback), pass the ball (typically to a Wide Receiver or Tight End), or run the ball.
Quarterbacks tend to have a strong arm for throwing the ball far and accurately.
Some quarterbacks are fast and are considered "dual threats" to pass or run.

@@

The football field is rectangular and is 120 yards long and 53 1/3 yards wide.
At each end of the 120-yard field is a team's end zone.
Each end zone is 10 yards long.
Thus, the distance from one end zone to the other end zone is 100 yards.
Behind each end zone is a field goal post.
A diagram of a football field is depicted in Figure @fig-footballField.

::: {#fig-footballField}
![](images/footballField.png)

A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the "red zone", where chances of scoring points are highest. The original figure was modified by adding field goal posts. (Figure retrieved from https://commons.wikimedia.org/wiki/File:American_football_field.svg)
:::

@@

The team with the ball (i.e., the offense) has four opportunities ("downs") to advance the ball 10 yards.
A team can advance the ball either by running it or passing and catching it.
At the end of a rushing play, the ball advances to wherever the ball carrier is tackled or goes out of bounds (i.e., wherever the player is "down").
At the end of a passing play, if the thrown ball is caught (i.e., a completed pass), the ball advances to wherever the ball carrier is tackled or goes out of bounds.
If the thrown ball is not caught (i.e., an incomplete pass), the ball does not advance.
Wherever the ball is advanced to dictates where the next play begins.
The yard position on the field where the next play takes place from is known as the "line of scrimmage".
Neither team can cross the line the line of scrimmage until the next play begins.
To begin the play, the ball is placed on the line of scrimmage and the Center gives (or "snaps") the ball to the Quarterback.

If the team advances the ball 10 or more yards within four downs, the team receives a "first down" and is awarded a new set of downs—four more downs to advance the ball 10 more yards.
If the team advances the ball all the way to the other team's end zone, they score a touchdown.
If the team fails to advance the ball 10 or more yards within four downs, the team loses the ball, and the other team takes possession at that spot on the field.
There are risks of giving the other team the ball with a short distance to score.
Thus, on fourth down, instead of trying to advance the ball for a first down, a team may choose to kick a field goal—to get points—or to punt.

@@

![Video that Provides an Introduction to Fantasy Football.](images/fantasyFootball.mp4){width=100%}
